Evolution of pre-copulatory and post-copulatory inbreeding behaviour \\ \vspace{10 mm} {\sffamily\Large\bfseries Supplemental results showing change in allele values over different parameter combinations, and allele values over generations for single replicates}

### 2017-08-19 Supplement.tex
Minor rewording of new figure legends
Minor tweaks

\noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect evolving phenotypic values for each trait over 40000 generations. Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02} show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates. Figures S\ref{rel_costs_01_03} and S\ref{rel_costs_01_02} show cost asymmetry simulations that do not appear in the main text. Figure S\ref{allcombs} summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}). Figure \ref{extra_MfPf} shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.}

@@

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.9]{figures/rel_costs_01_03.png}
\end{center}
\caption{Additional simulations with asymmetric direct costs, which are comparable to Figure 3 of the main text. These supplemental simulations support the general conclusion that costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy. Values in this figure reflect the same amount of cost asymmetry between traits, but with both traits having non-zero direct costs. Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.03$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.03$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free.}
\label{rel_costs_01_03}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.9]{figures/rel_costs_01_02.png}
\end{center}
\caption{Additional simulations with asymmetric direct costs, which are comparable to Figure 3 of the main text. These supplemental simulations support the general conclusion that costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy. Values in this figure reflect a smaller cost asymmetry between traits than simulated in the main text, with both traits having non-zero direct costs. Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free.}
\label{rel_costs_01_02}
\end{figure}

>>>>

\noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect evolving phenotypic values for each trait over 40000 generations. Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02} show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates. Figures S\ref{rel_costs_01_03} and S\ref{rel_costs_01_02} show cost asymmetry simulations that do not appear in the main text. Figure S\ref{allcombs} summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}). Figure S\ref{extra_MfPf} shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.}

@@

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.9]{figures/rel_costs_01_03.png}
\end{center}
\caption{Simulations with asymmetric direct costs, which are different but comparable to Figure 3 of the main text. These supplemental simulations support the general conclusion that costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy. Values in this figure reflect the same amount of cost asymmetry between traits, but with both traits having non-zero direct costs. Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.03$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.03$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free.}
\label{rel_costs_01_03}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.9]{figures/rel_costs_01_02.png}
\end{center}
\caption{Simulations with asymmetric direct costs, which are different but comparable to Figure 3 of the main text. These supplemental simulations support the general conclusion that costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy. Values in this figure reflect a smaller cost asymmetry between traits than simulated in the main text, with both traits having non-zero direct costs. Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free.}
\label{rel_costs_01_02}
\end{figure}
